
%\bibitem{Garfield01} Garfield, E. {\it Citation indexing: its theory and application in science, technology and humanities}. New York, Wiley, 1979, p. 23. 

%\bibitem{Glanzel02} Zhang, Lin; Janssens, Frizo; Liang, Liming; Glanzel, Wolfgang.  Journal cross-citation analysis for validation and improvement of journal-based subject classification in bibliometric research. {\it Scientometrics}. 2010, Vol. 82, p. 687--706.
\bibitem{Glanzel02} Zhang, L.; Janssens, F.; Liang, L.; Glanzel, W.  Journal cross-citation analysis for validation and improvement of journal-based subject classification in bibliometric research. {\it Scientometrics}. 2010, Vol. 82, p. 687--706.

\bibitem{Leydesdorf01} Leydesdorf, L. Various methods for the mapping of science. {\it Scientometrics}. 1987, Vol. 11, Nos 5--6, p. 295--324.

\bibitem{Leydesdorf02} Leydesdorf, L. Clusters and maps of science journals based on bi-connected graphs in Journal Citation Reports. {\it Journal of Documentation}. 2004, Vol. 60, No. 4, p. 371--427.

\bibitem{Leydesdorf04} Leydesdorf, L. Indicators of structual change in the dynamics of science: Entropy statisitics of the SCI Journal Citation Reports. {\it Scientometrics}. 2002, Vol. 53, No. 1, p. 131--159.

\bibitem{Leydesdorf03} Leydesdorf, L. Can scientific journals be classified in terms of aggregated journal-journal citation relations using the Journal Citation Reports? {\it Journal of the American Society for Information Science and Technology}. 2006, Vol. 57, No. 5, p. 601--613.

\bibitem{Schildt01} Shildt, H. A.; Mattsson, J. T. A dense network sub-grouping algorithm for co-citation analysis and its implementation in the software tool Sitkis. {\it Scientometrics}. 2006, Vol. 67, No. 1, p. 143--163.

\bibitem{Bassecoulard01} Bassecoulard, E.; Zitt, M. Indicators in A Research Institute: A Multi-level Classification of Scientific Journals. {\it Scientometrics}. 1999, Vol. 44, No. 3, p. 323--345.

\bibitem{Glanzel01} Glanzel, W.; Schubert, A. A new classification scheme of science fields and subfields designed for scientometric evaluation purposes. {\it Scientometrics}. 2003, Vol. 56, No. 3, p. 357--367.

%\bibitem{Glanzel02} Zhang, Lin; Janssens, Frizo; Liang, Liming; Glanzel, Wolfgang.  Journal cross-citation analysis for validation and improvement of journal-based subject classification in bibliometric research. {\it Scientometrics}. 2010, Vol. 82, p. 687--706.

\bibitem{C-MChen01} Chen, C.-M.  Classification of Scientific Networks Using Aggregated Journal-Journal Citation Relation in the journal CItation Reports. {\it Journal of the American Society for Information and Technology} 2008, Vol. 59, No. 14, p. 2296--2304.

%\bibitem{Rosvall}  Rosvall, Martin; Bergstrom, Carl T. Maps of random walks on complex networks reveal community structure. {\it Proceedings of the National Academy of Sciences of the United States of America}. 2008, Vol. 105, No. 4, p. 1118--1123.
\bibitem{Rosvall}  Rosvall, M.; Bergstrom, C. T. Maps of random walks on complex networks reveal community structure. {\it Proceedings of the National Academy of Sciences of the United States of America}. 2008, Vol. 105, No. 4, p. 1118--1123.

\bibitem{Amano04} 天野晃, 児玉閲. 引用にもとづく雑誌クラスタリング法の開発. {\bf 情報メディア研究}. 2009, Vol. 7, No. 1, p. 63--73.

%\bibitem{Leydesdorff06} Leydesdorf, Loaet;  Hammarfelt, Bj\"{o}rn; Salah, Almila. The Structure of the Arts \& Humanities Citation Index: A Mapping on the Basis of Aggregated Citations Among 1,157 Journals. {\it Journal of the American Society for Information Science and Technology}. 2010, Vol. 62, No. 12, p. 2414--2426.
\bibitem{Leydesdorff06} Leydesdorf, L.;  Hammarfelt, B.; Salah, A. The Structure of the Arts \& Humanities Citation Index: A Mapping on the Basis of Aggregated Citations Among 1,157 Journals. {\it Journal of the American Society for Information Science and Technology}. 2010, Vol. 62, No. 12, p. 2414--2426.

\ifthenelse{\blind=0}{
\bibitem{Amano01}  天野晃. 自己組織化による{DNA}シークエンスの分類. {情報メディア学会第5回研究会 発表資料}. 2003, p. 5--8.
}{
\bibitem{Amano01}  dummy1.
}


% ページ終端の調整
\ifthenelse{\blind=0}{
\vspace{0mm}
}{
\vspace{170mm}
}

\ifthenelse{\blind=0}{
\bibitem{Amano02} Amano, K.; Nakamura, H.; Ichikawa, H. Self-organizing clustering: A novel non-hierarchical method for clustering large amount of DNA sequences. {\it Genome Informatics}. 2003, Vol. 14, p. 575--576.
}{
\bibitem{Amano02}  dummy2.
}

\ifthenelse{\blind=0}{
\bibitem{Amano03}  Amano, K.; Ichikawa, H.; Nakamura, H.; Numa, H.;  Fukami-Kobayashi, K.; Nagamura, Y.; Onodera, A. Self-organizing Clustering: Non-hierarchical Clustering for Large Scale DNA Sequence Data. {\it IPSJ Digital Courier}. 2007, Vol. 3, p. 193--197.
}{
\bibitem{Amano03}  dummy3.
}


\bibitem{Darr01}  Darroch, J. N.; Ratcriff, D. Genaralized Itarative Scaling for Log-Linear Models. {\it The Anals of Mathematical Statistics}. 1972, Vol. 43, No. 5, p. 1470--1480.

\bibitem{eigen1}Eigenfactor$^{TM}$ Score and AI$^{TM}$ Score: Detailed methods. $<$http://www.eigenfactor.org/methods.pdf$>$ (accessed 2012-06-06).

\bibitem{Tsunoda1}角田裕之, 小野寺夏生. 論文と研究者のインパクトに対する新しい計量書誌学的指標 -論文引用グラフの固有ベクトル解析-. {\bf 情報メディア研究}. 2006, Vol. 5, p. 1-20.

\bibitem{google1}Google Page Rankの数理, Langville, Amy N.; Meyer, Carl D.  岩野和生, 黒川利明, 黒川洋 訳. 共立出版, 296ページ.

\bibitem{Onodera1}小野寺夏生. 新しい雑誌評価指標アイゲンファクターとは. 現代化学. 2009, Vol. 465, p. 38-42.

